MLH1 Data Report

### 2019-12-23 doc/Main_Report_Results.rmd
knit new version, did small tidying up

#### outgroups

The outgroups (SPIC and SPRET) don't show strong evidence of evolution in gwRR.

#### Male Patterns

Rapid evolution in musculus and molossinus; high and low CO count males (two instances of rapid gwRR evo, PWD and MSM)

#### Female Patterns

seems like female specific evolution in molossinus and musculus.
more variation in domesticus females.
Females have more nuanced patterns, there is strain specific differences.

@@

@@

## DMC1 Results

@@

@@

there is strain specific evolution for females ...

## Testing Normality Assumptions

## Permutations with equal sampling

@@

@@

### Another Heterochiasmy Plot

```{r HetC.plot22, echo=FALSE,  fig.width=10, fig.height=5, fig.caption="Sex-Specific MLH1 average"}

>>>>

@@

list out the points whic hsuport rapid male specific evolution for MLH1 rates.

@@

## DMC1 Results Spermatocytes

@@

### Testing Normality Assumptions

@@

## DMC1 Permutations with equal sampling

@@

insert male total sc results here

Nuanced
there is strain specific evolution for females ...

@@

```{r HetC.plot22, echo=FALSE,  fig.width=10, fig.height=5, fig.caption="Sex-Specific MLH1 average", eval=FALSE}
